The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-24 manuscript/manuscript.Rnw
add mouse lineage specific discussion

\begin{table}
<<mouse.lineage.specific,echo=FALSE,results="asis">>=
mou.all.lin.spec <-
    placenta.lineage.specific.table("mou.all",
                                    lineage.table=human.mouse.linage.specific.analysis)
setkey(mou.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in \mouse
  as compared to all other analyzed species.}
\label{tab:mouse_lineage_specific}
\end{table}

@@

>>>>

@@

% \paragraph{\mouse Lineage Specific Genes}

\begin{table}
  \footnotesize
<<mouse.lineage.specific,echo=FALSE,results="asis">>=
mou.all.lin.spec <-
    placenta.lineage.specific.table("mou.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40
                                    )
setkey(mou.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{\mouse}{all other analyzed species}}
\label{tab:mouse_lineage_specific}
\end{table}

Using a mixed-effects linear model to account for repeated testing of
\human and \mouse, we identified multiple genes which are
differentially expressed in the \mouse lineage in comparison to all
other lineages (\cref{tab:mouse_lineage_specific}). Notable
mouse-specific increases in expression include include genes like
\textit{Slc38a4} which are involved in nutrient transport and are
implicated in fetal growth restriction
\cite{Sharma.ea2016:Tpbpa-Cre-mediateddeletionofTFAP2C}.
